---
title: "HW4_Liang_Dan"
author: "Dan Liang"
date: "9/15/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Problem 3

1. show comparison from different aspects.
2. show causality, mechanism. explanation, and systematic structure. Different factors could be 
3. connected to explain one phenomena.
4. show multivariate data. It may uncover unexpected relationships with more features.
5. integrate different evidence to a graphic.
6. describe and document the evidence. A graphic should tell a complete story by itself.
7. present graphics with high-quality conten

# Problem 4

## 1.
```{r,echo=FALSE}
library(ggplot2)
library(ggExtra)
library(MASS)

library(ggplot2)
library(tidyr)
knitr::opts_chunk$set(echo = TRUE)

a <- read.csv("~/Desktop/HW4_data_1.csv")
b <- read.csv("~/Desktop/HW4_data_2.csv")
rawdata <- rbind(a,b)
summary(rawdata)
```
## 2.

The factors below will be presented:
1.block: groups of experiment trials
2.depth: one measurement
3.phosphate: one measurement

## 3.

```{r,echo=FALSE}
# create multipanel
CleanedData <- gather(rawdata,type,value = measurement, depth,phosphate)
CleanedData_n <- transform(CleanedData, block = as.factor(block))
CleanedData_n <- transform(CleanedData_n, type = as.factor(type))
ggplot(CleanedData_n, aes(x=block, y=measurement, fill=type))+geom_boxplot()
c <- data.frame(cbind(a$depth ,b$phosphate))
# scatterBarNorm(c, xlab=expression(italic(depth),ylab=expression(italic(phosphate))
```

```{r,echo=FALSE}
# create multipanel
attach(rawdata)
layout(matrix(c(1,1,2,3),2,2, byrow= TRUE))
hist (rawdata$depth, main="Hist of depth", xlab="depth", ylab="freq")
hist (rawdata$phosphate, main="Hist of phosphate", xlab="phosphate")
hist (rawdata$block, main="Hist of block", xlab="block", ylab="freq")
```

## 4.

```{r,echo=FALSE}
pairs(rawdata)
```


## 5

The block is not an output of an experiment, it is how manipulate the experiment. Two meastures follow normal distribution.


# Problem 5

```{r,echo=FALSE}
library (ggplot2)
# p <- ggplot(X, aes(X1, X2)) + geom_point() + theme_classic()
   # ggMarginal(p, X, type = "histogram", yparams=list(colour="orange"))

a <- read.csv("~/Desktop/HW4_data.csv") 
# plot(a$depth, a$phosphate, main= "Plot of a", xlab="depth", ylab="phosphate") 
p<- ggplot(a, aes(a$depth, a$phosphate))+ geom_point() + theme_classic()
ggMarginal(p, a, type = "histogram", yparams=list(colour="orange"))


```


