---
title: "HW5_Liang_Dan"
author: "Dan Liang"
date: "9/22/2018"
output: pdf_document
---

# Problem 3
```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, for a good figure, it should be concise and efffectively convey the message you want to let the audiance receive. Thus, decide what message you want to convey is important.  Also, a good figure is be able to demonstrate the trend or comparison of the data, also the details the audience interested in can be easily find. 

# Problem 4

## Part a

```{r}
Success <- function(vec){
    count <- sum(vec)
    return(count)
}
```
Computes the proportion of successes in a vector

## Part b

```{r}
set.seed(12345)
P4b_data <- matrix(rbinom(10, 1, prob = (30:40)/100), nrow = 10,
ncol = 10)
```

Matrix to simulate 10 flips of a coin with varying degrees of "fairness".

## Part c

```{r}
apply(P4b_data,MARGIN = 1, Success)

apply(P4b_data,MARGIN = 2, Success)
```


## Part d
```{r,include=FALSE}
GenerateRandom <- function(p){
    return(rbinom(10, 1, prob = p))
}

ProbList <- c(30:40)/100
ProbList <- matrix(ProbList, nrow = 1)

ResultMatrix <- apply(ProbList, MARGIN = 2 ,GenerateRandom)
row.names(ResultMatrix)<-c('E1','E2','E3','E4','E5','E6','E7','E8','E9','E10')
ResultMatrix
```


# Problem 5

```{r, echo=FALSE}
library("plot3D")
URL <- "http://www2.isye.gatech.edu/~jeffwu/book/data/starch.dat"
raw<-read.table(URL, header=T, skip=0, fill=T, stringsAsFactors = F)

#Starch_raw$starch <- as.factor(Starch_raw$starch)

G<-matrix(c('CA',1,'CO',2,'PO',3),ncol=2,byrow=T)
for (i in 1:length(raw$starch)) {
  if (raw$starch[i]%in%G[,1]) {
  raw$starch[i]=G[which(G[,1]==raw$starch[i]),2]
  }
}
x <- as.numeric(raw$starch)
y <- raw$strength
z <- raw$thickness

par(mfrow=c(1,3))
scatter3D(x, y, z, colvar = x, phi = 10, theta = 60, col = NULL, 
          breaks = c(0,1,2,3), xlab = 'Starch', ylab = 'Strength', zlab = 'Thickness')
scatter3D(x, y, z, colvar = x, phi = 0, theta = 0, col = NULL, 
          breaks = c(0,1,2,3), xlab = 'Starch', ylab = 'Strength', zlab = 'Thickness')
scatter3D(x, y, z, colvar = x, phi = 0, theta = 90, col = NULL, 
          breaks = c(0,1,2,3), xlab = 'Starch', ylab = 'Strength', zlab = 'Thickness')
```

# Problem 6

# Part a

Import a database of US cities and states
```{r, echo=FALSE}
library(downloader)
library(dplyr)
library(data.table)
download("http://www.farinspace.com/wp-content/uploads/us_cities_and_states.zip",
         dest = "us_cities_states.zip")
unzip("us_cities_states.zip", exdir = "~/Desktop/HW/uscities")
states <- fread(input = "~/Desktop/HW/uscities/us_cities_and_states/states.sql",
                skip = 19, sep = "'", sep2 = ",", header = F, select = c(2,4))
colnames(states) <- c('State','abbr')

cities1 <- fread(input = "./us_cities_and_states/cities.sql",
                skip = 19, sep = "'", sep2 = ",", header = F, select = c(2,4))
cities2 <- fread(input = "./us_cities_and_states/cities_extended.sql",
                skip = 19, sep = "'", sep2 = ",", header = F, select = c(2,4))

cities <- rbind(cities1,cities2)
colnames(cities) <- c('City','State')

CleanCities <- cities %>%
    group_by(City, State) %>%
    filter(row_number() == 1) %>%
    ungroup()

# Part b

CityNum <- table(CleanCities$State)
CityNum <- CityNum[-40]
CityNum <- CityNum[-8]
CityNum
```


# Part c

```{r, echo=FALSE}
LetterCount <- function(string){
    LetterList <- c('a','b','c','d','e','f','g','h','i','j','k','l','m','n','o','p','q','r','s','t','u','v','w','x','y','z')
    Result <- as.table(rep(0,26))
    row.names(Result) <- LetterList
    
    sp <- strsplit(tolower(as.character(string)), split="")[[1]]
    for(i in 1:26){
        Result[i] <- length(which(sp == LetterList[i]))
    }
    return(Result)
}

Results <- t(apply(as.matrix(states$State),MARGIN = 1,LetterCount))
Results <- Results[-8,]   # remove DC
head(Results)

temp <- apply(Results,MARGIN = 1, max)
ThreeLetterList <- floor(temp/3)
```

## Part d

```{r, echo=FALSE}
# https://cran.r-project.org/web/packages/fiftystater/vignettes/fiftystater.html
library(ggplot2)
library(fiftystater)
data("fifty_states") 
# this line is optional due to lazy data loading
crimes <- data.frame(state = tolower(rownames(USArrests)),
USArrests)

StateData <- cbind(crimes,CityNum)
StateData <- cbind(StateData,ThreeLetterList)


# map_id creates the aesthetic mapping to the state name
# column in your data
p <- ggplot(StateData, aes(map_id = state)) + # map points to the fifty_states shape data
geom_map(aes(fill = Freq), map = fifty_states) + expand_limits(x = fifty_states$long,
y = fifty_states$lat) + coord_map() + scale_x_continuous(breaks = NULL) +
scale_y_continuous(breaks = NULL) + labs(x = "", y = "") +
theme(legend.position = "bottom", panel.background = element_blank())
ggsave(plot = p, file ='HW5_Problem6_Plot_Dan.pdf')

p

```

The plot has been successfully saved in the file.

