---
title: "HW3_Liang_Dan"
author: "Dan Liang"
date: "9/16/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 4

The guides introduces good coding style, which includes readable, can be modified, shared easily. I think a good coding style starts with a clear logic of program, and lies in the uniformity of code. And good coding style needs practice. 


# Program 5


The code above gave back many suggestions. Some of them suggests that the code needs to be clearer.

# Program 6
```{r,echo=FALSE}
library(tidyverse)
library(beeswarm)
library(stargazer)
library(data.table)
library(knitr)
library(lubridate)
library(rmarkdown)
library(dplyr)
library(tidyr)
library(stargazer)
library(lintr) 
knitr::opts_chunk$set(echo = TRUE)


datasummary <- function (dev1,dev2){
  m1 <-mean(dev1)
  m2 <-mean(dev2)
  sd1<-sd(dev1)
  sd2<-sd(dev2)
  cov12<- cov(dev1, dev2)/sd1/sd2
  result <- data.frame(Mean1 = m1, Std1 = sd1, Mean2 = m2, Std2 = sd2, Corr = cov12)
  return (result)
}

LoadData <- readRDS ('HW3_data.rds')

   Observer <- NULL
   Mean1 <- NULL
   STD1 <- NULL
   Mean2 <- NULL
   STD2 <- NULL
   Correlation <- NULL

for (i in 1:13){
    Obs <- subset(LoadData,LoadData$Observer == i)
    statresult <- datasummary(Obs$dev1,Obs$dev2)
    Observer <- rbind(Observer, i)
    Mean1 <- rbind(Mean1, statresult$Mean1)
    STD1 <- rbind(STD1,statresult$Std1)
    Mean2 <- rbind(Mean2,statresult$Mean2)
    STD2 <- rbind(STD2,statresult$Std2)
    Correlation <- rbind(Correlation,statresult$Corr)
}

OutputResult <- data.frame(Observer = Observer, Mean1 = Mean1, Std1 = STD1, Mean2 = Mean2, 
                        Std2 = STD2, Cov = Correlation)

knitr::kable(OutputResult, caption="Data set Summary")

# create boxplot mean1  
boxplot(OutputResult$Mean1,
            main= toupper("Mean1 Boxplot"), 
            xlab="Dev1", ylab="Mean")
# create boxplot mean2
boxplot(OutputResult$Mean2,
            main= toupper("Mean2 Boxplot"), 
            xlab="Dev2", ylab="Mean")

 #create volin plot sd from dev1
library (vioplot)
library (sm)

x1 <- OutputResult$Std1
vioplot(x1, names=c("STD1"), 
   col="green")
title("STD1 Violin Plot")

#create volin plot sd from dev2
library(vioplot)
library(sm)

x2 <- OutputResult$Std2
vioplot(x2, names=c("STD2"), 
   col="green")
title("STD2 Violin Plot")
 
```


# Problem 7


```{r}
# url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BloodPressure.dat"
# the url link can not be assessed, data set can not be found
# BloodPressure<-read.table(url, header=T, skip=1, fill=T, stringsAsFactors = F)
# colnames(BloodPressure)<-c("Day",paste("Device",1:3,sep="_"),"Day2",paste("Doctor",1:3,sep="_"))
# BloodPressurecleaned <- select(BloodPressure,-Day2) %>%gather(Approach,Value,Device_1:Doctor_3) %>% arrange(Day)

# knitr::kable(summary(BloodPressurecleaned), caption="Blood Pressure summary")
```

Data link is broken, can not be assessed, the data cannot be find, the code has listed above.

# Problem 8

```{r,echo=FALSE}
fx <- function(x){
    y <- 3^x - sin(x) + cos(5*x)
    return(y)
}

fx_deri <- function(x){
    y <- log(3)*3^x - cos(x) - 5*cos(5*x)
    return(y)
}

x <- 0:1000/1000
y <- fx(x)
plot(x,y)

func <- function(Min,Max,Tolerance){
    set.seed(1)
    InitValue <- runif(1,min=Min,max=Max)
    tolerance <- Tolerance
    error <- 1
    X1 <- InitValue
    while (error > tolerance){
        X2 <- X1 - fx(X1)/fx_deri(X1)/100
        error <- abs(X2-X1)
        X1 <- X2
    }
    return(X2)
    
answer <- func (0,1,0.001)
answer
}
```




            






